\textsc{Second-order state-constraint Hamilton-Jacobi equations}

### 2021-02-04 Drafts and notes/Draft.tex
editing

%============%============%============%============%
%\setlength{\columnseprule}{0.4pt}
%\setlength{\topmargin}{0cm}
%\setlength{\oddsidemargin}{.25cm}
%\setlength{\evensidemargin}{.25cm}
%\setlength{\textheight}{22.5cm}
%\setlength{\textwidth}{15.5cm}
\renewcommand{\baselinestretch}{1.05}
%============%============%============%============%
\usepackage[toc,page]{appendix}
%============%============%============%============%
\usepackage{xcolor}
\usepackage{placeins}
\usepackage{amsfonts,amsmath,amsthm}
\usepackage{amssymb,epsfig}
\usepackage{enumerate} 
\usepackage[notcite,notref]{showkeys}
\usepackage{fullpage}
%============%============%============%============%
\usepackage[utf8]{inputenc}
%\usepackage{mathpazo}
%\usepackage[euler-digits]{eulervm}
\usepackage[libertine,cmintegrals,cmbraces,vvarbb]{newtxmath}
\usepackage{eucal}
\usepackage[unicode=true]{hyperref}
\hypersetup{colorlinks = true}
%\hypersetup{hidelinks=true}
\hypersetup{
     colorlinks,
     linkcolor={black!10!red},
     linkbordercolor = {black!100!red},
%    <your other options...>,
     citecolor={blue}
}

@@

\section{Preliminaries}\label{sec:prelim}
\subsection{Gradient estimate}

@@

\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps}.
\end{thm}

\begin{proof} For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$. 
\begin{figure}[ht]
    \centering
    %\incfig{Domains}
    \def\svgwidth{0.47\columnwidth}
    \import{./figs/}{Domains.pdf_tex}
    \caption{The domain $\Omega$ variations $\Omega_\delta, \Omega^\delta$.}
    \label{fig:Domains}
\end{figure}
We consider $\delta$ small enough so that the distance function $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is $\mathrm{C}^2$ in the strip $\Omega^\delta\backslash \overline{\Omega}_\delta$, we recall that $|D d(x)| = 1$ in that region. We extend the signed distance function into a $\mathrm{C}^2(\mathbb{R}^n)$ function, denoted by $d(x)$ such that 
\begin{equation*}
    \begin{cases}
    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_\delta,\\
    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^\delta\backslash \Omega.
    \end{cases}
\end{equation*}
We can choose $d(\cdot)$ so that $\Omega_\delta = \{x\in \mathbb{R}^n: d(x)-\delta >0 \}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: d(x) +\delta>0\}$.

\noindent To find candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the ansatz
\begin{equation}\label{eq:ansatz}
    u(x) = C_0 d(x)^{-\alpha}, \qquad x\in \Omega
\end{equation}
as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$. Let us plug \eqref{eq:ansatz} into \eqref{eq:PDEeps} we obtain that the highest order terms are
\begin{equation*}
        -C_0 \alpha(\alpha+1)d^{-(\alpha+2)} + C_0^p \alpha^p d^{-(\alpha+1)p}.
\end{equation*}
Setting them to zero, we deduce that
\begin{equation*}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_0 = \frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}.
\end{equation*}
We can obtain the following families of supersolution on $\Omega_\delta$ and subsolution on $\Omega^\delta$ as follow.
\begin{equation*}
        \overline{w}_{\eta,\delta}(x) = \frac{C_0+\eta}{(d(x)-\delta)^\alpha} +\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega_\delta \qquad\text{and}\qquad \underline{w}_{\eta,\delta}(x) = \frac{C_0-\eta}{(d(x)+\delta)^\alpha} -\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega^\delta.
\end{equation*}
We divide the rest of the proof into 3 steps. We first construct a minimal solution, then a maximal solution to \eqref{eq:PDEeps}, and finally show that they are equal to conclude the existence and uniqueness of solution to \eqref{eq:PDEeps}.

\begin{prop}\label{pro:minimalsol} There exists a minimal solution $\underline{u}\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that $v\geq \underline{u}$ for any other solution $v\in \mathrm{C}^2(\Omega)$ solving \eqref{eq:PDEeps}.
\end{prop}
\begin{proof} Let $w_{\eta,\delta}\in \mathrm{C}^2(\Omega)$ solves
    \begin{equation}\label{e:w_def}
    \begin{cases}
        \mathcal{L}\left[w_{\eta,\delta}\right] = 0 &\qquad\text{in}\;\Omega,\\
        \qquad w_{\eta,\delta} = \underline{w}_{\eta,\delta} &\qquad\text{on}\;\partial\Omega.
    \end{cases}
    \end{equation}
    Fix $\eta>0$, as $\delta\to 0$ the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary, therefore by comparison principle we have $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\leq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.

>>>>

%============%============%============%============%
%\setlength{\columnseprule}{0.4pt}
%\setlength{\topmargin}{0cm}
%\setlength{\oddsidemargin}{.25cm}
%\setlength{\evensidemargin}{.25cm}
%\setlength{\textheight}{22.5cm}
%\setlength{\textwidth}{15.5cm}
\renewcommand{\baselinestretch}{1.05}
%============%============%============%============%
\usepackage[toc,page]{appendix}
%============%============%============%============%
\usepackage{xcolor}
\usepackage{placeins}
\usepackage{amsfonts,amsmath,amsthm}
\usepackage{amssymb,epsfig}
\usepackage{enumerate} 
\usepackage[notcite,notref]{showkeys}
\usepackage{fullpage}
%============%============%============%============%
\usepackage[utf8]{inputenc}
%\usepackage{mathpazo}

%\usepackage[libertine,cmintegrals,cmbraceFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfs,vvarbb]{newtxmath}
\usepackage{eucal}
\usepackage[euler-digits]{eulervm}
\usepackage[unicode=true]{hyperref}
\hypersetup{colorlinks = true}
%\hypersetup{hidelinks=true}
\hypersetup{
     colorlinks,
     linkcolor={black!10!red},
     linkbordercolor = {black!100!red},
%    <your other options...>,
     citecolor={blue}
}

@@

\section{Preliminaries}\label{sec:prelim} 
\subsection{Setting and simplifications} Let $\Omega$ be an open, bounded and connected subset of $\mathbb{R}^n$ with boundary $\partial$ is of class $C^2$. For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) > \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$. 
\begin{figure}[ht]
    \centering
    %\incfig{Domains}
    \def\svgwidth{0.47\columnwidth}
    \import{./figs/}{Domains.pdf_tex}
    \caption{The domain $\Omega$ variations $\Omega_\delta, \Omega^\delta$.}
    \label{fig:Domains}
\end{figure}
We consider $\delta$ small enough so that the distance function $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is $\mathrm{C}^2$ in the strip $\Omega^\delta\backslash \overline{\Omega}_\delta$, we recall that $|D d(x)| = 1$ in that region. We extend the signed distance function into a $\mathrm{C}^2(\mathbb{R}^n)$ function, denoted by $d(x)$ such that 
\begin{equation*}
    \begin{cases}
    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_\delta,\\
    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^\delta\backslash \Omega.
    \end{cases}
\end{equation*}
We can choose $d(\cdot)$ so that $\Omega_\delta = \{x\in \mathbb{R}^n: d(x)-\delta >0 \}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: d(x) +\delta>0\}$.

Let $\delta_0>0$ be a fixed number such that $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is of class $\mathrm{C}^2$ on $\Omega\backslash \Omega_{\delta_0}$, i.e., in the region where $0<\mathrm{dist}(x,\partial\Omega) \leq \delta_0$. We then extend $\mathrm{dist}(x,\partial\Omega)$ to a function $d(x)\in \mathrm{C}^2(\mathbb{R}^n)$ such that 
\begin{equation*}
    \begin{cases}
    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_{\delta_0},\\
    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^{\delta_0}\backslash \Omega.
    \end{cases}
\end{equation*}
Let us denote
\begin{equation*}
    K := \max_{x\in \overline{\Omega}} |\Delta d(x)|.
\end{equation*}
\noindent Let us denote by $\mathcal{L}^\varepsilon:\rmC^2(\Omega)\to \rmC^2(\Omega)$ the operator
\begin{equation*}
    \mathcal{L}^\varepsilon[u](x) := \lambda u(x) + H(x,Du(x)) - \varepsilon \Delta u(x), \qquad x\in \Omega.
\end{equation*}
\subsection{Gradient estimate}

@@

\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u^\varepsilon\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that
\begin{equation*}
    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{\lambda} \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{\lambda} 
    \lim_{d(x)\to 0} u^\varepsilon(x) \,d(x)^\alpha = C_\varepsilon 
\end{equation*}
where
\begin{equation*}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}}.
\end{equation*}
\end{thm}

\begin{proof}

\noindent To find a candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the \emph{ansatz}
\begin{equation}\label{eq:ansatz}
    u(x) = C_\varepsilon d(x)^{-\alpha}, \qquad x\in \Omega
\end{equation}
as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$. Let us plug \eqref{eq:ansatz} into \eqref{eq:PDEeps} we obtain that 
\begin{align*}
    \lambda u(x) &\approx C_\varepsilon d(x)^{-\alpha},\\
    \frac{\partial u}{\partial x_i}(x) &\approx -\alpha C_\varepsilon d(x)^{-(\alpha+1)} \frac{\partial d}{\partial x_i}(x) \qquad\qquad\qquad \Longrightarrow\qquad |Du (x)|^p \approx \alpha^p C_\varepsilon^p d(x)^{-p(\alpha+1)}|\nabla d(x)|^p,\\
    %\frac{\partial^2 u}{\partial x_i^2}(x) &\approx \alpha(\alpha+1)C_0 d(x)^{-(\alpha+2)}\left|\frac{\partial d}{\partial x_i}(x)\right|^2 -\alpha C_0 d(x)^{-(\alpha+1)}\frac{\partial ^2 d}{\partial x_i^2}(x),\\
    \varepsilon\Delta u(x) &\approx \frac{\varepsilon C_\varepsilon\alpha(\alpha+1)}{d(x)^{\alpha+2}}|\nabla d(x)|^2 - \frac{\varepsilon C_\varepsilon\alpha}{d(x)^{\alpha+1}}\Delta d(x).
\end{align*}
As $|\nabla d(x)| = 1$ for $x$ near $\partial\Omega$, we see that as $x\to \partial \Omega$, the highest explosive order terms are
\begin{equation*}
        -\varepsilon C_\varepsilon \alpha(\alpha+1)d^{-(\alpha+2)} + C_\varepsilon^p \alpha^p d^{-(\alpha+1)p}.
\end{equation*}
Setting them to zero, we deduce that
\begin{equation*}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}}.
\end{equation*}
We can obtain the following families of supersolution on $\Omega_\delta$ and subsolution on $\Omega^\delta$ as follow. Let us denote
\begin{equation*}
    G = \left[\left(K\delta_0+(\alpha+1)\right)^\frac{1}{p-1} - (\alpha+1)^{\frac{1}{p-1}}\right]\alpha.
\end{equation*}

\begin{lem}\label{lem:subsln} For each $<\delta < \frac{1}{2}\delta_0$, if $\color{red}\eta\geq G\varepsilon^{\frac{1}{p-1}}$,\color{black} we have
\begin{equation*}
    \overline{w}_{\eta,\delta}(x) = \frac{C_\varepsilon+\eta}{(d(x)-\delta)^\alpha} +\frac{M}{\lambda},\qquad x\in \Omega_\delta
\end{equation*}
is a supersolution of \eqref{eq:PDEeps} in $\Omega_\delta$ where
\begin{equation*}
    M = \max_{\overline{\Omega}} f(x) + 2^{\alpha+1}K\alpha\varepsilon\delta_0^{-(\alpha+1)}.
\end{equation*}
\end{lem}
\begin{proof} We compute
\begin{align*}
    \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) &= \frac{\lambda(C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} + M_\eta + \frac{(C_\varepsilon+\eta)^p \alpha^p}{(d(x)-\delta)^{p(\alpha+1)}}|\nabla d(x)|^p - f(x) \\
    &\qquad\qquad\qquad\qquad\quad\;\,  - \frac{\varepsilon(C_\varepsilon+\eta)\alpha(\alpha+1)}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^2 + \frac{\varepsilon(C_\varepsilon+\eta)\alpha}{(d(x)-\delta)^{\alpha+1}}\Delta d(x).
\end{align*}
\textcolor{red}{to be filled in...}
\end{proof}

\begin{lem}\label{lem:supersln} For each $\eta>0$ there exists $M_\eta > 0$ such that 
\begin{equation*}
    \overline{w}_{\eta,\delta}(x) \textcolor{orange}{(\underline{w}_{\eta, \delta})} = \frac{C_\varepsilon-\eta}{(d(x)+\delta)^\alpha} -\frac{M_\eta}{\lambda}, \qquad x\in \Omega^\delta 
\end{equation*}
is a supersolution $\textcolor{orange}{(subsolution)}$ of \eqref{eq:PDEeps} in $\Omega^\delta$.
\end{lem}

We divide the rest of the proof into 3 steps. We first construct a minimal solution, then a maximal solution to \eqref{eq:PDEeps}, and finally show that they are equal to conclude the existence and uniqueness of solution to \eqref{eq:PDEeps}.

\begin{prop}\label{pro:minimalsol} There exists a minimal solution $\underline{u}\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that $v\geq \underline{u}$ for any other solution $v\in \mathrm{C}^2(\Omega)$ solving \eqref{eq:PDEeps}.
\end{prop}
\begin{proof} Let $w_{\eta,\delta}\in \mathrm{C}^2(\Omega)$ solves
    \begin{equation}\label{e:w_def}
    \begin{cases}
        \mathcal{L}\left[w_{\eta,\delta}\right] = 0 &\qquad\text{in}\;\Omega,\\
        \qquad w_{\eta,\delta} = \underline{w}_{\eta,\delta} &\qquad\text{on}\;\partial\Omega.
    \end{cases}
    \end{equation}
    Fix $\eta>0$, as $\delta\to 0$ the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary, therefore by comparison principle we have $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\geq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.
